Self Regulation Ontology Retest Analyses

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring

```{r warning=FALSE, message=FALSE}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p1 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"),
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  mutate(dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p2 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75)+
  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"),
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

mylegend<-g_legend(p2)

p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 24, height = 20, units = "in", dpi = 100)
rm(tmp, labels, p1, p2 , p3)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Variance_Breakdown_Plot.jpg')
```

@@

@@

```{r}
sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/var_breakdown_summary.doc")
```

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value, na.rm=T),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n),
         sem_pct = sd_pct/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Between subject variance",
                               "Within subject variance",
                               "Error variance")), mean_pct))+
  geom_errorbar(aes(ymin=cil, ymax=ciu, group=task), position=position_dodge(width = 0.25), width=0.25, size=2, alpha = 0.85, color="gray")+
  geom_point(position=position_dodge(width = 0.25), size=3, aes(color=task, shape=task))+
  #geom_bar(position=position_dodge(width = 0.5), width=0.5, aes(fill=task), stat='identity', alpha=0.5)+
  #geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent of total variance')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12),
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  ylim(0,100)+
  labs(caption = str_wrap("FIGURE 5:  Percentage of variance explained by each of the three sources of variance: between subjects, within subjects (between sessions) and error variance for 1000 bootstrapped samples. Error bars are 95% confidence intervals.", width = 120))

ggsave('Variance_Breakdown_DotPlot.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures", width = 7, height = 4, units = "in", dpi = 300)
```

>>>>

```{r echo=FALSE, out.width='100%'}
fig_name = 'Variance_Breakdown_Plot.jpeg'

@@

```{r}
rm(var_subs_pct_by_task_model, var_ind_pct_by_task_model, var_resid_pct_by_task_model)
```

@@

@@

```{r echo=FALSE, out.width='100%'}
fig_name = 'Variance_Breakdown_DotPlot.jpeg'
